\documentclass{article}
\usepackage{graphicx} % Required for inserting images

\title{SmartCalc}
\author{Raik410 (ernaratt)}
\date{December 2023}

\begin{document}

\maketitle

\section{Introduction}

SmartCalc is an advanced calculator application designed to offer both speed and versatility for a variety of mathematical operations. Its efficiency is largely attributed to the implementation of Reverse Polish Notation (RPN) and an optimized stack-based computation method, allowing for rapid and accurate calculations.

\section{Features}

\subsection{Algebraic and Geometric Calculations}

SmartCalc excels in handling a wide range of algebraic and geometric calculations. It simplifies complex expressions and solves various algebraic equations, extending its utility to geometric problem-solving.

\subsection{Advanced Mathematical Functions}

SmartCalc supports an extensive array of advanced mathematical functions, enhancing its utility for various scientific and engineering tasks:

\begin{itemize}
    \item Computes cosine: \texttt{cos(x)}
    \item Computes sine: \texttt{sin(x)}
    \item Computes tangent: \texttt{tan(x)}
    \item Computes arc cosine: \texttt{acos(x)}
    \item Computes arc sine: \texttt{asin(x)}
    \item Computes arc tangent: \texttt{atan(x)}
    \item Computes square root: \texttt{sqrt(x)}
    \item Computes natural logarithm: \texttt{ln(x)}
    \item Computes common logarithm: \texttt{log(x)}
\end{itemize}

\subsection{Graph Plotting}

The ability to plot graphs of functions visually represents how mathematical functions behave, making it an invaluable tool for both educational and professional use.

\subsection{Credit Calculator}

A dedicated module for calculating credit payments makes SmartCalc a versatile tool for financial planning, allowing users to compute various parameters related to credit and loans.

\subsection{User Interface and Manual Input}

With its user-friendly interface, SmartCalc caters to a broad audience. The support for manual input ensures that it is as intuitive as traditional calculators.

\section{Build System and Makefile Targets}

SmartCalc's build system includes several targets in its `Makefile` for ease of development and maintenance:

\begin{itemize}
    \item \texttt{all}: Compiles the entire project.
    \item \texttt{install}: Installs the compiled application.
    \item \texttt{uninstall}: Removes the installed application.
    \item \texttt{clean}: Cleans up build files.
    \item \texttt{dvi}: Generates documentation in DVI format.
    \item \texttt{dist}: Creates a distribution package of the project.
    \item \texttt{test}: Runs the test suite.
    \item \texttt{gcov\_report}: Generates a test coverage report.
\end{itemize}

\section{Conclusion}

SmartCalc is not just a calculator; it's a comprehensive tool for a wide range of mathematical and financial calculations, boasting a user-friendly interface and advanced features. It's designed to cater to the needs of students, educators, and professionals alike.

\end{document}